STAT 253 Final Project - Classification Models

### 2022-11-02 Final_Project_Classification_Models.Rmd
Maybe finished random forest model

imdb_clean_class <- imdb_clean %>%
  mutate(success_ratio = revenue/budget) %>%
  mutate(flop = as.factor(ifelse(success_ratio > 1, 'FALSE', 'TRUE'))) %>%
  filter(!is.na(flop))

@@

# Recipe
data_rec <- recipe(flop ~ No_of_Votes, data = imdb_clean_class) %>%
  step_naomit()

# Workflows
data_wf_mtry5 <- workflow() %>%
  add_model(rf_spec %>% set_args(min_n = 5)) %>%
  add_recipe(data_rec)

@@

data_wf_mtry10 <- workflow() %>%
  add_model(rf_spec %>% set_args(min_n = 10)) %>%
  add_recipe(data_rec)

data_wf_mtry25 <- workflow() %>%
  add_model(rf_spec %>% set_args(min_n = 25)) %>%
  add_recipe(data_rec)

data_wf_mtry50 <- workflow() %>%
  add_model(rf_spec %>% set_args(min_n = 50)) %>%
  add_recipe(data_rec)
```

```{r}
# Fit Models
set.seed(123) # make sure to run this before each fit so that you have the same 1000 trees
data_fit_mtry5 <- fit(data_wf_mtry5, data = imdb_clean_class)

# Fit models for 10, 25, and 50
set.seed(123) 
data_fit_mtry10 <- fit(data_wf_mtry10, data = imdb_clean_class)

set.seed(123)
data_fit_mtry25 <- fit(data_wf_mtry25, data = imdb_clean_class)

set.seed(123) 
data_fit_mtry50 <- fit(data_wf_mtry50, data = imdb_clean_class)
```

@@

data_rf_OOB_output <- bind_rows(
    rf_OOB_output(data_fit_mtry5,5, imdb_clean_class %>% pull(flop)),
    rf_OOB_output(data_fit_mtry10,10, imdb_clean_class %>% pull(flop)),
    rf_OOB_output(data_fit_mtry25,25, imdb_clean_class %>% pull(flop)),
    rf_OOB_output(data_fit_mtry50,50, imdb_clean_class %>% pull(flop))
)

@@

```{r}
rf_OOB_output(data_fit_mtry50,50, imdb_clean_class %>% pull(flop)) %>%
    conf_mat(truth = class, estimate= .pred_class)
```

@@

model_output <-data_fit_mtry50 %>% 
    extract_fit_engine()

@@

model_output2 <- data_wf_mtry50 %>% 
  update_model(rf_spec %>% set_args(importance = "permutation")) %>% #based on permutation
  fit(data = imdb_clean_class) %>% 
    extract_fit_engine()

>>>>

imdb_clean_class <- imdb_clean %>%
  mutate(success_ratio = revenue/budget) %>%
  mutate(flop = as.factor(ifelse(success_ratio > 1.5, 'FALSE', 'TRUE'))) %>%
  filter(!is.na(flop))

@@

# Recipe
data_rec <- recipe(flop ~ No_of_Votes, Runtime, IMDB_Rating, Meta_score, Genre, popularity, vote_average, vote_count,
                   data = imdb_clean_class) %>%
  step_naomit()

# Workflows
data_wf_mtry150 <- workflow() %>%
  add_model(rf_spec %>% set_args(min_n = 150)) %>%
  add_recipe(data_rec)

@@

data_wf_mtry125 <- workflow() %>%
  add_model(rf_spec %>% set_args(min_n = 125)) %>%
  add_recipe(data_rec)

data_wf_mtry75 <- workflow() %>%
  add_model(rf_spec %>% set_args(min_n = 75)) %>%
  add_recipe(data_rec)

data_wf_mtry100 <- workflow() %>%
  add_model(rf_spec %>% set_args(min_n = 100)) %>%
  add_recipe(data_rec)
```

```{r}
# Fit Models
set.seed(123) # make sure to run this before each fit so that you have the same 1000 trees
data_fit_mtry150 <- fit(data_wf_mtry150, data = imdb_clean_class)

# Fit models for 10, 25, and 50
set.seed(123) 
data_fit_mtry125 <- fit(data_wf_mtry125, data = imdb_clean_class)

set.seed(123)
data_fit_mtry75 <- fit(data_wf_mtry75, data = imdb_clean_class)

set.seed(123) 
data_fit_mtry100 <- fit(data_wf_mtry100, data = imdb_clean_class)
```

@@

data_rf_OOB_output <- bind_rows(
    rf_OOB_output(data_fit_mtry150,150, imdb_clean_class %>% pull(flop)),
    rf_OOB_output(data_fit_mtry125,125, imdb_clean_class %>% pull(flop)),
    rf_OOB_output(data_fit_mtry75,75, imdb_clean_class %>% pull(flop)),
    rf_OOB_output(data_fit_mtry100,100, imdb_clean_class %>% pull(flop))
)

@@

```{r}
rf_OOB_output(data_fit_mtry125,125, imdb_clean_class %>% pull(flop)) %>%
    conf_mat(truth = class, estimate= .pred_class)
```

@@

model_output <-data_fit_mtry125 %>% 
    extract_fit_engine()

@@

model_output2 <- data_wf_mtry125 %>% 
  update_model(rf_spec %>% set_args(importance = "permutation")) %>% #based on permutation
  fit(data = imdb_clean_class) %>% 
    extract_fit_engine()
